---
title: "p8105_hw1_yb2584"
author: "Yunshen Bai"
date: '2023-09-18'
output: html_document
---
# Problem 1
## 1.Set up

```{r setup,warning = FALSE, message = FALSE}
library(tidyverse)
library(moderndive)
```
```{r, include=FALSE}
Sys.setlocale(category = "LC_ALL",locale = "English_United States")
```

## 2.Load data


```{r }
data("early_january_weather")
```

## 3.Describe data

First, let's see the first 20 lines of this data set

```{r pressure, echo=FALSE}
head(early_january_weather,20)
```

This data set recorded the weather of EWR in 2013 from Jan 1 to Jan 15.The variables include `r names(early_january_weather)`.This data set includes `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. From this data set, the average temperature of EWR is `r mean(early_january_weather$temp)`. Therefore, we can conclude that EWR is very hot from January 1 to January 15.

Now we use scatter plot to show the trend of temperature and humid change in these 15 days
```{r}
ggplot(data = early_january_weather,aes(x=time_hour,y=temp))+geom_point(aes(color=humid))
ggsave("Plot1_HW1.jpg")
```

# Problem 2

The names of random normal sample, logical vector, character vector and factor vector are "nor_sam", "log_vec", "cha_vec", "fac_vec"
```{r}
nor_sam=rnorm(10)
log_vec=nor_sam>0
cha_vec=c("ch1","ch2","ch3","ch4","ch5","ch6","ch7","ch8","ch9","ch10")
fac_vec=factor(c("easy","hard","normal","normal","hard","normal","hard","easy","hard","easy"))
dt=tibble(nor_sam,log_vec,cha_vec,fac_vec)
show(dt)
```

Next, I use "mean" function to calculate the mean of each variable
```{r}
mean(pull(dt,nor_sam))
mean(pull(dt,log_vec))
mean(pull(dt,cha_vec))
mean(pull(dt,fac_vec))
```
Therefore, "mean" function works on random normal sample and logical vector, doesn't work on character vector and factor vector.

Then, I will apply the "as.numeric" function to the logical, character, and factor variables, and try to calculate their mean. 
```{r}
as.numeric(log_vec)
as.numeric(cha_vec)
as.numeric(fac_vec)
mean(as.numeric(log_vec))
mean(as.numeric(cha_vec))
mean(as.numeric(fac_vec))
```
Form the result,for the logical vector, "as.numeric" function will turn True into 1 and False into 0. For the factor vector, "as.numeric" function will transform different factors as increasing level, start as 1. Therefore, we can calculate their mean when we apply "as.numeric" function to logical vector and factor vector. However, "as.numeric" function doesn't work on character vector, we can not calculate the mean of a character vector.
