---
title: "p8105_hw1_yb2584"
author: "Yunshen Bai"
date: '2023-09-18'
output: html_document
---
# Problem 1
## 1.Set up

```{r setup,warning = FALSE, message = FALSE}
library(tidyverse)
library(moderndive)
```
```{r, include=FALSE}
Sys.setlocale(category = "LC_ALL",locale = "English_United States")
```

## 2.Load data


```{r }
data("early_january_weather")
```

## 3.Describe data

First, let's see the first 20 lines of this data set

```{r pressure, echo=FALSE}
head(early_january_weather,20)
```

This data set recorded the weather of EWR in 2013 from Jan 1 to Jan 15.The variables include `r names(early_january_weather)`.This data set includes `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. From this data set, the average temperature of EWR is `r mean(early_january_weather$temp)`. Therefore, we can conclude that EWR is very hot from January 1 to January 15.

Now we use scatter plot to show the trend of temperature and humid change in these 15 days
```{r}
ggplot(data = early_january_weather,aes(x=time_hour,y=temp))+geom_point(aes(color=humid))
ggsave("Plot1_HW1.jpg")
```

